Spin canonical rings of log stacky curves

### 2015-07-03 stacky_write_up/spin_cring.tex
cleaned up todos

\todo{Make sure we want to have linear equivalence $\sim$ of divisors instead of $=$ in most places}
\todo{Write all block orders as tensors so we don't need to say the $y_i$ precede the $x_i$.}
\todo{It's a bit strange how many tables are split across pages. Can we we make sure they each lie on a single page. Robin: do this at the end, not yet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup of
$PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations. \todo{Peter: In the abstract we say finite area.  Don't we want that here as well?}  
We consider the graded {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$ \todo{Peter: Is $k$ bad to use here, since we will implicitly later use $k$ as the base field? Robin: Perhaps, although modular forms are traditionally referred to as having weight $k$. Not sure on this one.}. One of the best
ways to understand the ring of modular forms is to give a
presentation as a quotient of a polynomial ring.
%of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
To do so, it is useful to have a bound on the
degrees in which the generators and relations can occur. In the
special case that $\Gamma$ has no odd weight modular forms, Voight
and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
We extend their result to all Fuchsian groups $\Gamma$ in the main
theorem of this work.

@@

\noindent
with multiplication structure corresponding to tensor product of
sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
\cong \proj R$ \todo{Peter: I'm confused.  Why is this only true when $g\geq 2$? Robin: see statement of Petri's theorem (which actually usually assumes $g \geq 4$)...}. When $g \geq 2$, Petri's theorem gives generators
and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
is generated in degree 1 with relations in degree 2, as shown in
\cite[p. 157]{saint-donat:proj} and Arbarello--Cornalba--Griffiths--Harris
\cite[Section 3.3]{acgh:algebraic-curves}. This has the pleasant 
geometric consequence that all such canonically embedded curves are
scheme theoretically cut out by degree 2 equations.

@@

In particular, we bound the degrees of generators and relations of a
log spin canonical ring. Let
$\sx$ be a stacky curve with signature $\sigma = (g; e_1, \ldots,
e_r; \delta)$. The application of O'Dorney's work to log spin
canonical rings gives a weak bound in the case $g = 0$ in
terms of the least common multiples of the $e_i$'s \cite[Chapter 5]
{dorney:canonical}. In their treatment of log spin canonical
rings, Voight and Zureick-Brown bounded generator degrees by $3 \cdot \max(e_1, \ldots, e_r)$
and relation degrees by $6 \cdot \max(e_1, \ldots, e_r)$ when $\halfcan$ is effective
\cite[Corollary 10.4.6]{vzb:stacky}. \todo{Peter: Seems a bit misleading by misrepresenting VZB's work; in reality they found fairly tight bounds in the case they worked in. Robin: How? This solely talks about their work for the log spin canonical rings which is clearly NOT tight. They give a larger bound than us for a subset of the cases we check...}

@@

\begin{rem}
\label{rem:main-weaker-assumptions}
In fact, the proof of Theorem ~\ref{thm:main} holds not only for log spin canonical divisors, which must have distinct points, but also for arbitrary effective divisors
$\Delta$. \todo{Peter: $\Delta$ seems weird as the name of the divisor, since its typically reserved for log divisors.  Also, how is this true?  This only follows given sufficient base point freeness conditions.  It is true when $g=0$ if that's what you meant to say. Robin: Throughout VZB, for example, $\Delta$ is used to represent any effective divisor. Where does an assumption that $\Delta$ has coefficient $1$ come into play?} Furthermore, one may relax the assumption that $k$ is perfect. Instead, one only need assume that the stacky curve
is separably rooted, i.e. the residue field at each stacky point
is separable.
\end{rem}
\todo{Peter: This remark seems to say two very separate things.  Why are they in the same remark? Robin: This remark describes how the weaker conditions for which the theorem also holds.}

Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.  In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two we have to explicitly construct specific base cases and present a finite list of exceptional cases, while in the high genus case we deduce base cases from more general arguments.
\begin{rem}
\label{rem:explicit-generators}
The proofs of the main theorems in the low genus cases not only
obtain bounds on the degrees of the generators and relations, but
also yield explicit systems of generators and an explicit initial ideal of
relations. Furthermore, our proof of the high genus case also
provides an inductive procedure for explicitly determining the 
generators and initial ideal of relations of log spin canonical
rings. Many explicit systems of generators and relations are
detailed in interesting low genus examples by Neves
\cite[Section III.4]{neves:halfcan}.  \todo{Peter: The statement about the high genus case seems a bit unclear/misleading Robin: how so}

Furthermore, explicit constructions also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
Specifically, in almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
\end{rem}  \todo{Peter: Again, why are these two sections of the remark grouped together? Robin: Isn't this remark describing whether the theorem gives explicit constructions and tight bounds? Those seem pretty related...}

%The main theorem of this paper, Theorem ~\ref{thm:main}, combined
%with a lemma of Voight and Zureick-Brown \cite[Lemma 10.2.1]
%{vzb:stacky}, provides a statement on all rings of modular forms.
Together with a theorem from Voight and Zureick-Brown \cite
[Theorem 9.3.1]{vzb:stacky} 
%and \cite[Theorem 9.3.1]{vzb:stacky}, 
\todo{Peter: The paragraph used to be confusingly redundant.  I think I fixed it but read through the commented out stuff to make sure it says the correct thing. Robin: Why are you ignoring Lemma 10.2.1 as well as its connection to Kodaira--Spencer? These are necessary.}
we have the following application to
rings of modular forms. 
%Note that the lemma from Voight and Zureick-
%Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
%from the classical work of Kodaira--Spencer
%\cite{kodaira-spencer:deformations}.

@@

If $M_k(\Gamma) = 0$ for all odd $k$, then the ring of modular
forms $M(\Gamma)$ is generated as a $\BC$-algebra by elements of
degree at most $3 \cdot \max(3, e_1, \ldots, e_r)$ with relations
generated in degrees at most $6 \cdot \max(3, e_1, \ldots, e_r)$.\todo{Peter: Are you sure it shouldn't be $6e$ and $12e$, because he showed the {\emph canonical ring} has the bounds $3e$ and $6e$, which would mean the {\emph half-canonical} ring should have bounds $6e$ and $12e$ right? Robin: I think you are correct, although don't use $e$ since it is max(3, ...) instead of max(5, ...)}

@@

\begin{rem}
In the case that $M_k(\Gamma) = 0$ for all odd $k$, the generation bound of $3 \cdot \max(3, e_1, \ldots, e_r)$ and relation
bound of $6 \cdot \max(3, e_1, \ldots, e_r)$ can be reduced to $\max(3,e_1, \ldots, e_r)$ and $2 \cdot \max(3,e_1, \ldots, e_r)$, apart from several small families of cases. See 
~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[Theorem 9.3.1]{vzb:stacky} for a more precise statement of these bounds.
\end{rem}

@@

\ssec{Stacky Curves and Log Spin Canonical Rings}
\label{ssec:stacky-background}
A \textbf{stacky curve} $\sx$ over a field $k$ is a smooth proper
geometrically-connected Deligne-Mumford stack of dimension $1$ over
$k$ with a dense open subscheme. A stacky curve is \textbf{tame} if
its stabilizers are coprime to char $k$.

\begin{rem}
\label{rem:stack-formalism}
Stacky curves may be formally defined in the language of stacks, (as
is done in the works of Voight and Zureick-Brown \cite{vzb:stacky},
Abramovich and Vistoli \cite{abramovich-vistoli:compactifying}, and
Behrend and Noohi \cite{behrend-noohi:uniformization},) but for the
purposes of this paper, it suffices to treat $\sx$ as a scheme
whose associated divisor group has a finite number of stacky
points.

In this paper, all stacky curves are assumed to be tame and
$k$ will is assumed to be algebraically closed. We also assume that the
stacky curves are separably rooted, i.e. the residue field of each
of the stacky points is separable.  \todo{Peter: We should clarify this last statement.  If we are assuming $k$ is algebraically closed, aren't the points automatically separably-rooted?  Really aren't we saying if perfect, then restrict to algebraically closed, and if not, everything works similarly as long as separably rooted? Robin: Yes I guess $k$ being algebraically closed implies perfectness... we can use a similar statement to Remark 5.5.7 from VZB}

With this stacks-theoretic description in mind, the remainder of this paper is primarily phrased using the language
of Weil divisors.
\end{rem}

If $P_1, \ldots, P_r$ are the stacky points of a stacky curve $\sx$,
then we use $e_1, \ldots, e_r \in \BZ_{\geq 2}$ to denote the orders
of the stabilizer groups of the points with non-trivial
stabilizers. We call $e_i$ the \textbf{stabilizer order} of $P_i$.
In order to study objects associated with stacky curves, it is often
useful to consider them in the context of schemes (instead of in the context of stacks).

\begin{defn}
\label{defn:coarse-space}
Let $\sx$ be a stacky curve over $k$ with coarse space $X$ \todo{We haven't defined a course space yet.  Confusingly, this definition is labeled ``defn:course-space'' which made me think it was supposed to.} and stacky points $P_1, \ldots,
P_r$ with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$.
Let $X$ be a nonsingular projective (algebraic) curve over $k$ of
genus $g$. Then, we notate
\[
	\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
\]
\end{defn}

We can equip stacky curves with a log divisor $\Delta$ that is a 
sum of distinct points each with trivial stabilizer. \todo{Peter: It isn't necessary in the proof that these log points be non-stacky, even though only such log divisors arise from modular forms.  Need we say that?  If so, then we should explicitly note that these are the only cases that arise.} A divisor
$\Delta$ of this form is called a \textbf{log divisor}. We use
$\delta := \deg \Delta$ to refer to the degree of the log divisor.
If $\sx$ has coarse space $X$ of genus $g$, then we say $\sx$ has
\textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$.

@@

A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is
called a \textbf{log stacky curve} and the study of their
canonical rings is the main focus of the work by Voight and Zureick-
Brown \cite{vzb:stacky}. For this paper, we consider \textbf{log
spin curves} which are triples $(\sx, \Delta, \halfcan)$ where $\sx$
is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di
\sx$ satisfies $2 \halfcan \sim K_X + \Delta + \sum_{i = 1}^{r}
\frac{e_i - 1}{e_i} P_i$. Such a divisor $\halfcan$ is called a
\textbf{log spin canonical divisor} on $(\sx, \Delta)$. We use
$\halfcan_X := \lfloor L \rfloor $ to refer to the \textbf{spin
canonical divisor} (also known as the half-canonical divisor, semi-
canonical divisor, or theta characteristic) \todo{Peter: I think we mismatched the parenthetical.  Also, why did we define the spin canonical divisor of $\halfcan_X$ especially.  Isn't it really just a special case of the definition before. Robin: How? the parenthetical encompasses all alternate names! Yes it's a special case, but we never give it a name otherwise. You could define it as the log spin canonical divisor with zero log divisor but that somehow doesn't seem to give the right picture.} associated to the
coarse space $X$ of $\sx$  (i.e. $\halfcan_X$ is a divisor such
that $2\halfcan_X \sim K_X + \Delta$). 
We define $H^0$ of a stacky divisor as follows:

@@

\todo{possibly compactify or refer to relations, Aaron: I think we should almost remove these definitions, and that these shouldn't be in environments. I suspect people will be familiar with them, or be able to look them up.}

@@

\begin{example}
\label{eg:base-0-377}
Let $(\sx,0, \halfcan')$ be a log spin curve with signature $\sigma =
(0; 3, 7, 7; 0)$ and $\halfcan' \sim -\infty + \frac{1}{3} P_1 +
\frac{3}{7} P_2 + \frac{3}{7} P_3,$ where $P_1,P_2,$ and $P_3$ are
distinct points. In this example, we will exhibit a minimal
presentation for $R' = R(\sx,0, \halfcan')$ and show the triple
$(\sigma, \halfcan' + \frac{3}{7} P_3, J = \{2, 3\},$) is admissible.
Notice that $\deg \lfloor d K_{\sx'} \rfloor= -d + \lfloor \frac{d}{3}
\rfloor + 2 \lfloor \frac{3d}{7} \rfloor$.

@@

Now, we check the admissibility of $J= \{2, 3\}$ (corresponding to the $e_2,e_3=7$). \todo{Robin: I don't understand your edit, Peter. Admissibility is not a property of $J$.} By relabelling the
variables if necessary, we can assume that $x_{7, 1}$ corresponds
to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
correspond to the generator with maximal pole order at $P_3$. Use
the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
\ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{custom:Ad-ii} We may also choose
pole orders of the generators such that $y_{i, e_i'}$ is the only
generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
generators lying below the line as seen in Figure ~\ref{fig:377}
(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
$x_{7, 2}$ respectively).

@@

\begin{align*}
	\dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / I\right)_d &=
	\dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ \initial(I)\right)_d \\
	&= \dim_k \left((k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle
	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_d
\end{align*}\todo{Peter: I think you need additional degree subscripts added to the polynomial ring or something, so this isn't infinite. Robin: Aren't there already existing degree subscripts?}

\noindent
for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k \left((k[x_{7, 2},
x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle x_{7, 2}^2, x_{5, 1}^2
\rangle\right)_d$ can be checked by looking at the $k$-basis at each degree
$d$.

@@

\begin{example}
\label{eg:exception-1-5}
Let $(\sx', 0, L')$ be a log spin curve of genus 1 so that $L' = P -
 Q + \frac{2}{5} P_1.$ Let $u \in (R_L)_1$ be any nonzero element \todo{Peter: I'm very confused.  There are no elements in degree 1...  Oh, I see, I think you mean $L'=\frac{2}{5}P_1$ (without the $P-Q$) maybe?}.
We obtain $\di u|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by Riemann
--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_\halfcan)_3$ be any nonzero
element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since
if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0
(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$. Finally,
let $y_5 \in (R_\halfcan)_5$ be an element with $y_5|_{P_1} = -P_1$. Then,
we claim there is some $\alpha \in k$ so that

$$R_\halfcan \cong k[u, y_3, y_5]/(y_3^4 - \alpha u y_5^2).$$

@@

\item[(b)] Choose an ordering $\prec$ on $k[u, x_1, \ldots, x_m]$ such that
	\[
		\ord_u(f) < \ord_u(h) \implies f\prec h.
	\]
	Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in
	Definition ~\ref{defn:graded-p-lex} and $k[u, x_1, \ldots, x_m, y_1,
	\ldots, y_n]$ with the block order giving the order giving $y_1, 
	\ldots, y_n$ precedence over $u, x_1, \ldots, x_m$.

	If $I'$ and $I$ are the ideals of relations of $k[u, x_1, \ldots, x_m]
	\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]
	\to R_{\halfcan}$ respectively, then

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%% High genus %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\todo{Make sure we want to have linear equivalence $\sim$ of divisors instead of $=$ in most places}
\todo{It's a bit strange how many tables are split across pages. Can we we make sure they each lie on a single page. Robin: do this at the end, not yet. Aaron: I changed our long tables to tables. Why did we use longtables at all? Our tables are all pretty short.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
Let $\Gamma$ be a {\bf Fuchsian} group, i.e. a discrete subgroup of
$PSL_2(\BR)$ acting on the upper half plane $\BH$ by fractional
linear transformations, such that $\Gamma \backslash \BH$ has finite area.
We consider the graded {\bf ring of modular forms}
$M(\Gamma) = \bigoplus_{k = 0}^\infty M_k(\Gamma)$ \todo{Peter: Is $k$ bad to use here, since we will implicitly later use $k$ as the base field? Robin: Perhaps, although modular forms are traditionally referred to as having weight $k$. Not sure on this one. Aaron: I do not think this will confuse anyone.}. One of the best
ways to understand the ring of modular forms is to give a
presentation as a quotient of a polynomial ring.
%of $M(\Gamma)$ for general Fuchsian groups $\Gamma$. 
To do so, it is useful to have a bound on the
degrees in which the generators and relations can occur. In the
special case that $\Gamma$ has no odd weight modular forms, Voight
and Zureick-Brown give tight bounds \cite[Chapters 7-9]{vzb:stacky}.
We extend their result to all Fuchsian groups $\Gamma$ in the main
theorem of this work.

@@

\noindent
with multiplication structure corresponding to tensor product of
sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
\cong \proj R$ \todo{Peter: I'm confused.  Why is this only true when $g\geq 2$? Robin: see statement of Petri's theorem (which actually usually assumes $g \geq 4$)... Aaron: You need genus at least 2 for $\Omega_X$ to be ample. There are mild generalizations of Petri's theorem, for example those in vzb, which also compute generators and relations for hyperelliptic curves, and curves of genus 3.}. When $g \geq 2$, Petri's theorem gives generators
and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
is generated in degree 1 with relations in degree 2, as shown in
\cite[p. 157]{saint-donat:proj} and Arbarello--Cornalba--Griffiths--Harris
\cite[Section 3.3]{acgh:algebraic-curves}. This has the pleasant 
geometric consequence that all such canonically embedded curves are
scheme theoretically cut out by degree 2 equations.

@@

In particular, we bound the degrees of generators and relations of a
log spin canonical ring. Let
$\sx$ be a stacky curve with signature $\sigma = (g; e_1, \ldots,
e_r; \delta)$. The application of O'Dorney's work to log spin
canonical rings gives a weak bound in the case $g = 0$ in
terms of the least common multiples of the $e_i$'s \cite[Chapter 5]
{dorney:canonical}. In their treatment of log spin canonical
rings, Voight and Zureick-Brown bounded generator degrees by $6 \cdot \max(e_1, \ldots, e_r)$
and relation degrees by $12 \cdot \max(e_1, \ldots, e_r)$ when $\halfcan$ is effective
\cite[Corollary 10.4.6]{vzb:stacky}. Note that the bounds we write here differ from those stated in Voight and Zureick-Brown \cite[Corollary 10.4.6]{vzb:stacky} by a factor of 2 because their grading convention differs from ours by a factor of 2.
\todo{Peter: Seems a bit misleading by misrepresenting VZB's work; in reality they found fairly tight bounds in the case they worked in. Robin: How? This solely talks about their work for the log spin canonical rings which is clearly NOT tight. They give a larger bound than us for a subset of the cases we check... Aaron: I think the point is that if they put in some more work, they could have reduced the bounds. However, I agree with Robin for two reasons: First, they didn't put in the work to get the tighter bounds. Second, even with a small amount of work, they would have only gotten bounds which are twice ours, as their grading is off from ours by a factor of two.}

@@

\begin{rem}
\label{rem:main-weaker-assumptions}
In fact, the proof of Theorem ~\ref{thm:main} holds not only for log spin canonical divisors, which must have distinct points, but also for arbitrary effective divisors
$\Delta$. \todo{Peter: $\Delta$ seems weird as the name of the divisor, since its typically reserved for log divisors.  Also, how is this true?  This only follows given sufficient base point freeness conditions.  It is true when $g=0$ if that's what you meant to say. Robin: Throughout VZB, for example, $\Delta$ is used to represent any effective divisor. Where does an assumption that $\Delta$ has coefficient $1$ come into play?} Furthermore, one may relax the assumption that $k$ is perfect. Instead, one only need assume that the stacky curve
is separably rooted, as described further in Remark ~\ref{rem:stack-formalism}.
\end{rem}

Theorem ~\ref{thm:main} is proven separately in the cases that the genus $g = 0, g = 1,$ and $g \geq 2$ in Theorems ~\ref{thm:g-0-main}, ~\ref{thm:g-1-main}, and ~\ref{thm:g-high-main}, respectively.  In each of these proofs, we follow a similar inductive process utilizing the lemmas of Section ~\ref{sec:induction}; however, in the first two we have to explicitly construct specific base cases and present a finite list of exceptional cases, while in the genus $g \geq 2$ case we deduce base cases from more general arguments.
\begin{rem}
\label{rem:explicit-generators}
The proofs of the main theorems in the low genus cases not only
obtain bounds on the degrees of the generators and relations, but
also yield explicit systems of generators and an explicit initial ideal of
relations. Furthermore, our proof of the genus $g \geq 2$ case also
provides an inductive procedure for explicitly determining the 
generators and initial ideal of relations of log spin canonical
rings. Many explicit systems of generators and relations for curves of genus $2 \leq g \leq 15$ are
detailed in interesting examples by Neves
\cite[Section III.4]{neves:halfcan}. 
\end{rem}
\begin{rem}
The explicit construction described in Remark ~\ref{rem:explicit-generators} also reveals that the bounds given in Theorem ~\ref{thm:main} are tight.
Specifically, in almost all cases, the log spin canonical ring requires a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree at least $2e-4$. 
Furthermore, there are many infinite families of cases which require a generator in degree $e = \max(5, e_1, \ldots, e_r)$ and a relation in degree exactly $2e$.
\end{rem}

Combining the main theorem of this paper, Theorem ~\ref{thm:main} with the main theorem from Voight and Zureick-Brown ~\cite
[Theorem 1.4]{vzb:stacky} and a minor Lemma \cite[Lemma 10.2.1]{vzb:stacky}
we have the following application to
rings of modular forms. 
%Note that the lemma from Voight and Zureick-
%Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
%from the classical work of Kodaira--Spencer
%\cite{kodaira-spencer:deformations}.

@@

If $M_k(\Gamma) = 0$ for all odd $k$, then the ring of modular
forms $M(\Gamma)$ is generated as a $\BC$-algebra by elements of
degree at most $6 \cdot \max(3, e_1, \ldots, e_r)$ with relations
generated in degrees at most $12 \cdot \max(3, e_1, \ldots, e_r)$.

@@

\begin{rem}
\label{rem:factor-two}
In the case that $M_k(\Gamma) = 0$ for all odd $k$, the generation bound of $6 \cdot \max(3, e_1, \ldots, e_r)$ and relation
bound of $12 \cdot \max(3, e_1, \ldots, e_r)$ can be reduced to $2\cdot \max(3,e_1, \ldots, e_r)$ and $4 \cdot \max(3,e_1, \ldots, e_r)$, apart from several small families of cases. See 
~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[Theorem 8.7.1]{vzb:stacky} for a more precise statement of these bounds in the cases that $g = 0$ and $g > 0$ respectively. Note that we multiply all bounds given in Voight and Zureick-Brown \cite{vzb:stacky} by a factor of two, because our grading convention on $\bigoplus_k M_k(\Gamma)$ differs from that of Voight and Zureick-Brown by a factor of 2.
\end{rem}

@@

\ssec{Stacky Curves and Log Spin Canonical Rings}
\label{ssec:stacky-background}
We begin by setting up the notation for stacky curves and canonical rings. Wherever possible, we opt for a more elementary scheme-theoretic approach, instead of a stack-theoretic one. See Remark ~\ref{rem:stack-formalism} for more details.

\begin{defn}
\label{defn:stacky-curve}
A \textbf{stacky curve} $\sx$ over an algebraically closed field $k$ is the datum of a smooth proper connected scheme $X$ of dimension $1$, together with a finite number of closed points of $X$, $P_1, \ldots, P_r$, called {\bf stacky points}, with {\bf stabilizer orders} $e_1, \ldots, e_r \in \BZ_{\geq 2}.$ The scheme $X$ associated to a stacky curve $\sx$ is called the {\bf coarse space} of $\sx$.

\end{defn}

\begin{rem}
\label{rem:stack-formalism}
Stacky curves may be formally defined in the language of stacks, as
is done in the works of Voight and Zureick-Brown \cite{vzb:stacky},
Abramovich and Vistoli \cite{abramovich-vistoli:compactifying}, and
Behrend and Noohi \cite{behrend-noohi:uniformization}.

The results of this paper can be easily couched in terms of the language of stacks. If one works over an arbitrary field $k$ (which need not be algebraically closed) one can extend Theorem ~\ref{thm:main} to hold in the case that the stacky curve $\sx$ is tame and separably rooted, i.e. the residue field of each
of the stacky points is separable.

With this stack-theoretic description in mind, the remainder of this paper is primarily phrased using the language
of schemes.
\end{rem}

\begin{defn}
\label{defn:div-ex}
Let $\sx$ be a stacky curve over $k$ with coarse space $X$ of genus $g$ and stacky points $P_1, \ldots,
P_r$ with stabilizer orders $e_1, \ldots, e_r \in \BZ_{\geq 2}$.
Then, we notate
\[
	\di \sx = \left(\bigoplus_{P\notin \{P_1, \ldots, P_r\}} \langle 
	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
\]
\end{defn}

We can equip stacky curves with a log divisor $\Delta$ that is a 
sum of distinct points each with trivial stabilizer. 
\todo{Peter: It isn't necessary in the proof that these log points be non-stacky, even though only such log divisors arise from modular forms.  Need we say that?  If so, then we should explicitly note that these are the only cases that arise. Aaron: I don't think we need to say it, the application to modular forms still goes through whether or not we want to assume they are distinct. I like keeping log divisors like this so that we parallel \cite{vzb:stacky}} 
A divisor
$\Delta$ of this form is called a \textbf{log divisor}. We use
$\delta := \deg \Delta$ to refer to the degree of the log divisor.
If $\sx$ has coarse space $X$ of genus $g$, then we say $\sx$ has
\textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$.

@@

A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is
called a \textbf{log stacky curve} and the study of their
canonical rings is the main focus of the work by Voight and Zureick-
Brown \cite{vzb:stacky}. For this paper, we consider \textbf{log
spin curves} which are triples $(\sx, \Delta, \halfcan)$ where $\sx$
is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di
\sx$ satisfies $2 \halfcan \sim K_X + \Delta + \sum_{i = 1}^{r}
\frac{e_i - 1}{e_i} P_i$. Such a divisor $\halfcan$ is called a
\textbf{log spin canonical divisor} on $(\sx, \Delta)$. Throughout the paper, we use
the notation $\halfcan_X := \lfloor L \rfloor.$ to refer to the log spin
canonical divisor (also known as the half-canonical divisor, 
semi-canonical divisor, or theta characteristic) associated to the
coarse space $X$ of $\sx.$  (i.e. $\halfcan_X$ is a divisor such
that $2\halfcan_X \sim K_X + \Delta$). 
We define $H^0$ of a stacky divisor as follows:

@@

@@

\begin{example}
\label{eg:base-0-377}
Let $(\sx',0, \halfcan')$ be a log spin curve with signature $\sigma =
(0; 3, 7, 7; 0)$ and $\halfcan' \sim -\infty + \frac{1}{3} P_1 +
\frac{3}{7} P_2 + \frac{3}{7} P_3,$ where $P_1,P_2,$ and $P_3$ are
distinct points. In this example, we will exhibit a minimal
presentation for $R' = R(\sx',0, \halfcan')$ and show the triple
$(\sigma, \halfcan' + \frac{3}{7} P_3, J = \{2, 3\},$) is admissible.
Notice that $\deg \lfloor d K_{\sx'} \rfloor= -d + \lfloor \frac{d}{3}
\rfloor + 2 \lfloor \frac{3d}{7} \rfloor$.

@@

Now, we check the admissibility of $(\sx', L' ,J),$ where $J = \{2, 3\}$. By relabelling the
variables if necessary, we can assume that $x_{7, 1}$ corresponds
to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
correspond to the generator with maximal pole order at $P_3$. Use
the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
\ref{custom:Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{custom:Ad-ii} We may also choose
pole orders of the generators such that $y_{i, e_i'}$ is the only
generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
generators lying below the line as seen in Figure ~\ref{fig:377}
(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
$x_{7, 2}$ respectively).

@@

\begin{align*}
	\dim_k \left(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I\right)_d &=
	\dim_k \left(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]	/ \initial(I)\right)_d \\
	&= \dim_k \left(k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle
	x_{7, 2}^2, x_{5, 1}^2 \rangle \right)_d
\end{align*}
\noindent
for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k \left(k[x_{7, 2},
x_{7, 1}, x_{5, 1}, x_{3, 1}] / \langle x_{7, 2}^2, x_{5, 1}^2
\rangle\right)_d$ can be checked by looking at the $k$-basis at each degree
$d$.

@@

\begin{example}
\label{eg:exception-1-5}
Let $(\sx', 0, L')$ be a log spin curve of genus 1 so that $L' = P -
 Q + \frac{2}{5} P_1.$ Let $x_2 \in (R_L)_2$ be any nonzero element.
We obtain $\di x_2|_{P_1} = 0,$ since $2P - 2Q \sim 0$ and by Riemann
--Roch, $\dim_k (P_L)_2 = 1.$ Let $y_3 \in (R_\halfcan)_3$ be any nonzero
element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since
if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0
(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$. Finally,
let $y_5 \in (R_\halfcan)_5$ be an element with $y_5|_{P_1} = -P_1$. Then,
we claim there is some $\alpha \in k$ so that

$$R_\halfcan \cong k[x_2 , y_3, y_5]/(y_3^4 - \alpha x_2 y_5^2).$$

@@

\item[(b)] Choose an ordering $\prec$ on $k[u, x_1, \ldots, x_m]$ such that
	\[
		\ord_u(f) < \ord_u(h) \implies f\prec h.
	\]
	Equip $k[y_1, \ldots, y_n]$ with graded $P$-lex, as defined in
	Definition ~\ref{defn:graded-p-lex} and $k[y_1, \ldots, y_n] \otimes k[u, x_1, \ldots, x_m]$ with block order.
	If $I'$ and $I$ are the ideals of relations of $k[u, x_1, \ldots, x_m]
	\to R_{\halfcan'}$ and $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]
	\to R_{\halfcan}$ respectively, then

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus $\geq 2$ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Genus $\geq 2$}
\label{sec:g-high}
We now consider the case when the genus is at least 2. In this case, we are able to bound the degrees of generators of $R_\halfcan$ and its ideal of relations. In this section, we do not obtain explicit presentations of $R_\halfcan.$  This contrasts Sections ~\ref{sec:g-1} and ~\ref{sec:g-0} where we not only obtain bounds, but also obtain inductive presentations. The tradeoff is that in the genus 0 and 1 cases, we have to account for with explicit base cases, whereas in this section we apply general results.
